Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-16 Master Thesis/synopsis.tex
Name chapters & sections
Update 2.5

\chapter{Synopsis}

\section{Some Results on the valuation spectra}

@@

@@

\begin{proof}
Let $G_\ell$ be an pro-$\ell$-Sylow group of $G_K$. By the ramification theory for general valuations ([E], §20) we have $G_\ell\cong\mathbb{Z}_\ell(1)^r\rtimes G_k(\ell)$ where the action is defined via the cyclotomic character and $r = \dim_{\mathbb{F}_\ell}(\Gamma/\ell\Gamma)$. In particular, $r\leq 2$ and $G_k(\ell)$ is the pro-$\ell$-Sylow group of $G_k$ hence $G_k(\ell)\cong \mathbb{Z}_\ell$ or $G_k(\ell) \cong 1$.

Let $G_K(\ell)$ be the maximal pro-$\ell$-quotient of $G_K$. Since $\mu_\ell\subset K$, the action of $G_k$ on the pro-$\ell$-Sylow group of the inertia group of $w$ factors through $G_k(\ell)$. We see that the canonical projection $G_K\to G_K(\ell)$ is an isomorphism. Therefore we have:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \cong\mathrm{H}^3(G_K(\ell),\mathbb{Z}/\ell\mathbb{Z}) \cong\mathrm{H}^3(G_\ell,\mathbb{Z}/\ell\mathbb{Z}) \]
Now the equivalence of (i) and (ii) follows from [Se], Ch. I, §4.

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$.
\end{proof}

@@

@@

@@

\paragraph{} Let $k$ and $k'$ be the algebraic closures of $\mathbb{Q}$ in $K$ and $K'$ respectively, i.e. the constant fields of $K$ and $K'$, and let $\overline{k}$ and $\overline{k'}$ be the algebraic closure of $k$ and $k'$ in $\overline{K}$ and $\overline{K'}$ respectively.

@@

@@

>>>>

\chapter{Valuations}

\section{The Valuation Spectra}

@@

\section{The Main Lemma}

@@

\begin{proof}
Let $G_\ell$ be an pro-$\ell$ Sylow group of $G_K$. By the ramification theory for general valuations ([E], §20) we have $G_\ell\cong\mathbb{Z}_\ell(1)^r\rtimes G_k(\ell)$ where the action is defined via the cyclotomic character and $r = \dim_{\mathbb{F}_\ell}(\Gamma/\ell\Gamma)$. In particular, $r\leq 2$ and $G_k(\ell)$ is the pro-$\ell$-Sylow group of $G_k$ hence $G_k(\ell)\cong \mathbb{Z}_\ell$ or $G_k(\ell) \cong 1$.

Let $G_K(\ell)$ be the maximal pro-$\ell$-quotient of $G_K$. Since $\mu_\ell\subset K$, the action of $G_k$ on the pro-$\ell$-Sylow group of the inertia group of $w$ factors through $G_k(\ell)$. We see that the canonical projection $G_K\to G_K(\ell)$ is an isomorphism. Therefore we have:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \cong\mathrm{H}^3(G_K(\ell),\mathbb{Z}/\ell\mathbb{Z}) \cong\mathrm{H}^3(G_\ell,\mathbb{Z}/\ell\mathbb{Z}) \]
Now the first assertion follows from [Se], Ch. I, §4.

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $(\Gamma':\Gamma)< \infty$ and $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 1 and 2).
\end{proof}

@@

\chapter{Correspondences}

@@

Let $k$ and $k'$ be the algebraic closures of $\mathbb{Q}$ in $K$ and $K'$ respectively, i.e. the constant fields of $K$ and $K'$, and let $\overline{k}$ and $\overline{k'}$ be the algebraic closure of $k$ and $k'$ in $\overline{K}$ and $\overline{K'}$ respectively.

@@

@@

\chapter{Theorem}

\section{Free-By-Finite Groups}

@@

\section{Admissible Sets}
